### 2025-06-19 basic-statistics.qmd
20250618 - include quantiles

player_stats_seasonal %>% 
  dplyr::select(age, years_of_experience, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        CV = ~ sd(., na.rm = TRUE) / mean(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

@@

The formula for the correlation coefficient is in @sec-correlation.

>>>>

player_stats_seasonal %>% 
  dplyr::select(age, years_of_experience, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        q10 = quantile(., .10, na.rm = TRUE), # 10th quantile
        q90 = quantile(., .90, na.rm = TRUE), # 90th quantile
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        CV = ~ sd(., na.rm = TRUE) / mean(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

@@

The formula for the correlation coefficient is in @eq-pearsonCorrelation.

### 2025-06-19 correlation.qmd
20250618 - include quantiles

```{r}
player_stats_seasonal %>% 
  dplyr::select(height, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        CV = ~ sd(., na.rm = TRUE) / mean(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

>>>>

```{r}
player_stats_seasonal %>% 
  dplyr::select(height, fantasyPoints) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        q10 = quantile(., .10, na.rm = TRUE), # 10th quantile
        q90 = quantile(., .90, na.rm = TRUE), # 90th quantile
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        CV = ~ sd(., na.rm = TRUE) / mean(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

### 2025-06-19 multiple-regression.qmd
20250617 - fix duplicate identifier
20250618 - include quantiles

### Load Data {#sec-correlationLoadData}

@@

```{r}
player_stats_seasonal %>% 
  dplyr::select(fantasyPoints, age, height, weight, target_share) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

>>>>

### Load Data {#sec-multipleRegressionLoadData}

@@

```{r}
player_stats_seasonal %>% 
  dplyr::select(fantasyPoints, age, height, weight, target_share) %>% 
  dplyr::summarise(across(
      everything(),
      .fns = list(
        n = ~ length(na.omit(.)),
        missingness = ~ mean(is.na(.)) * 100,
        M = ~ mean(., na.rm = TRUE),
        SD = ~ sd(., na.rm = TRUE),
        min = ~ min(., na.rm = TRUE),
        max = ~ max(., na.rm = TRUE),
        q10 = quantile(., .10, na.rm = TRUE), # 10th quantile
        q90 = quantile(., .90, na.rm = TRUE), # 90th quantile
        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
        IQR = ~ IQR(., na.rm = TRUE),
        MAD = ~ mad(., na.rm = TRUE),
        median = ~ median(., na.rm = TRUE),
        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
        skewness = ~ psych::skew(., na.rm = TRUE),
        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
      .names = "{.col}.{.fn}")) %>%
    tidyr::pivot_longer(
      cols = everything(),
      names_to = c("variable","index"),
      names_sep = "\\.") %>% 
    tidyr::pivot_wider(
      names_from = index,
      values_from = value)
```

### 2025-06-19 simulation.qmd
20250618 - typo
20250618 - include quantiles

#### Run the Bootsrapping Simulation {#sec-simulationProjectedPointsBootstrappingRun}

@@

bootstrappedFantasyPoints_summary <- bootstrappedFantasyPoints %>% 
  group_by(id) %>% 
  summarise(
    mean = mean(projectedPoints, na.rm = TRUE),
    SD = sd(projectedPoints, na.rm = TRUE),
    q10 = quantile(projectedPoints, .10), # 10th quantile
    q90 = quantile(projectedPoints, .90), # 90th quantile
    min = min(projectedPoints, na.rm = TRUE),
    max = max(projectedPoints, na.rm = TRUE),
    range = max(projectedPoints, na.rm = TRUE) - min(projectedPoints, na.rm = TRUE),
    IQR = IQR(projectedPoints, na.rm = TRUE),
    MAD = mad(projectedPoints, na.rm = TRUE),
    CV = SD/mean,
    median = median(projectedPoints, na.rm = TRUE),
    pseudomedian = DescTools::HodgesLehmann(projectedPoints, na.rm = TRUE),
    mode = petersenlab::Mode(projectedPoints, multipleModes = "mean"),
    skewness = psych::skew(projectedPoints, na.rm = TRUE),
    kurtosis = psych::kurtosi(projectedPoints, na.rm = TRUE)
  )
```

>>>>

#### Run the Bootstrapping Simulation {#sec-simulationProjectedPointsBootstrappingRun}

@@

bootstrappedFantasyPoints_summary <- bootstrappedFantasyPoints %>% 
  group_by(id) %>% 
  summarise(
    mean = mean(projectedPoints, na.rm = TRUE),
    SD = sd(projectedPoints, na.rm = TRUE),
    min = min(projectedPoints, na.rm = TRUE),
    max = max(projectedPoints, na.rm = TRUE),
    q10 = quantile(projectedPoints, .10, na.rm = TRUE), # 10th quantile
    q90 = quantile(projectedPoints, .90, na.rm = TRUE), # 90th quantile
    range = max(projectedPoints, na.rm = TRUE) - min(projectedPoints, na.rm = TRUE),
    IQR = IQR(projectedPoints, na.rm = TRUE),
    MAD = mad(projectedPoints, na.rm = TRUE),
    CV = SD/mean,
    median = median(projectedPoints, na.rm = TRUE),
    pseudomedian = DescTools::HodgesLehmann(projectedPoints, na.rm = TRUE),
    mode = petersenlab::Mode(projectedPoints, multipleModes = "mean"),
    skewness = psych::skew(projectedPoints, na.rm = TRUE),
    kurtosis = psych::kurtosi(projectedPoints, na.rm = TRUE)
  )
```
